Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-08-20 surfaces-write-up/arXiv-versions/surface-write-up-arXiv-v1.tex
surfaces: various minor rewordings, add arXiv1

\usepackage{amsmath}
\usepackage{amsxtra}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{mathrsfs}
\usepackage{subfiles}
\usepackage{euler}
\usepackage{hyperref}
\usepackage{color}
\usepackage{longtable}
\usepackage{float}
\usepackage{caption}
\usepackage{thmtools}
\usepackage{thm-restate}

@@

In Section \ref{sec:proj} we prove the following two results bounding
the degree of generators and relations of
stacky canonical rings on $\bp^m$:
\begin{restatable}{thm}{restateeffective}
\label{thm:proj-effective-intro}
Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, with $\alpha_i =
\frac{c_i}{k_i} \in \bq_{> 0}$ and let each $D_i \in \di \bp^m$ be an integral divisor.

@@

\begin{restatable}{thm}{restateproj}
\label{thm:proj-generators-relations}
Let $D =
\sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ 
with $\alpha_i = \frac{c_i}{k_i}\in \bq.$ Let $\bp^m \cong \proj \bk[x_0,\ldots, x_m]$ with
$f_0, \ldots, f_n \in \bk[x_0, \ldots, x_m]$ such that
for $1 \leq i \leq n$ we have $D_i = V(f_i)$ and $\deg(f_i) = a_i.$
Further, after reordering the terms of $D$, and possibly adding in
$D_i$ with coefficient $\alpha_i = 0$, assume that $f_0,\ldots, f_m$ are independent linear
polynomials in $x_0, \ldots, x_m$. 
Define 
\[\ell_i = \lcm_{j\ne i}(k_j).\] 
Then $R_D$ is generated in degrees at most 
\[
	\sum_{i=0}^n \ell_i a_i
\]

\noindent
with relations generated in degrees at most
\[
	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0\le i \le n}
	(	\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
\]
\end{restatable}
\begin{rem}\label{rem:proj-tight-bounds} Note that the bounds
	given in Theorem ~\ref{thm:proj-effective-intro}
are tight and are typically attained, as explained in
Remark ~\ref{rem:exact-effective-bounds}.
Additionally, the bounds given in Theorem 
~\ref{thm:proj-generators-relations} are asymptotically
tight to within a factor of two 
for the following class of divisors. Consider
a divisor 
$ D = \sum_{i=0}^n\frac{p_i}{2q_i}H_i \in \bq \otimes_\bz \di \bp^m$
such that $H_i$ are hyperplanes,  
$q_i$ are pairwise coprime integers, and $p_i$ are chosen
so that $\deg D = \frac{1}{2 \prod_{i=0}^n}q_i$. Further,
choose a linear subspace $\pi: \bp^1 \rightarrow \bp^m$  generically so that
$\pi^* D = \sum_{i=0}^n \frac{p_i}{2q_i}P_i$, 
where $P_i$ are distinct points in $\bp^1$. To choose such a map
$\pi$, we may need to assume that the base field is infinite.
Note that by the Remark immediately following Theorem 8 in 
\cite{dorney:canonical},
the given bounds on the generators and relations of
$R_{\pi^*D}$ are within
a factor of two of the degree of generation and relations of
$R_{\pi^*D}$. Finally, since restriction map
$R_D \rightarrow R_{\pi^*D}$ induced by the restriction maps
on cohomology $H^0(\bp^m, dD) \rightarrow H^0(\bp^1, \pi^*(dD))
\cong H^0(\bp^1, d\pi^* D)$ are surjective, we obtain that
the bounds for the generators and relations of $R_D$ given in
Theorem ~\ref{thm:proj-generators-relations} also
agree with the degree of generation and relations 
to within a factor of two.
 \end{rem}

In Section \ref{sec:hirz}, we shift our attention to Hirzebruch surfaces. Recall that for each $m \geq 0$ we can define the
Hirzebruch surface $F_m := \proj(\sym^\bullet \sco_{\bp^1} \oplus
\sco_{\bp^1}(m)),$ or as a quotient of an open subscheme of
$\ba^4$ by a 
weighted action, as is done in the
beginning of Section \ref{sec:hirz}.
Note that Hirzebruch surfaces are regular, normal,
and locally factorial, being $\bp^1$ bundles over
$\bp^1$, and therefore the natural map from Cartier
divisors to Weil divisors is an isomorphism.
In other words, all Cartier divisors arise as the zero locus
of a section of some line bundle. We implicitly use this in the
statement of the following theorem. The analogous fact for
projective space was also implicitly used in Theorems
~\ref{thm:proj-effective-intro} and ~\ref{thm:proj-generators-relations}.

@@

\noindent
span $H^0(\bp^m, dD)$ over $\bk$. Furthermore, functions 
of the form $u^d \cdot \prod_{i=0}^n f_i^{c_i}$ satisfying Equation \ref{align:pm-span} and
\begin{align}
\label{align:pm-basis}
c_i = -\lfloor d\alpha_i \rfloor && \text{ for } && i > m
\end{align}

@@

\begin{rem}
\label{rem:proj-two-points}
Note that we cannot extend this result to the case when
$D$ is supported at two hypersurfaces with arbitrary rational (non-effective)
coefficients in the same manner that O'Dorney does for the
$\bp^1$ case \cite[Section 4]{dorney:canonical}. As will be shown
in Example ~\ref{eg:hyperplane}, the degrees of generation of the
canonical ring of a general $\bq$-divisor supported on two
hyperplanes cannot be bounded so tightly. The two-point
$\bp^1$ result leverages the fact that $\bp^1$ has precisely two
independent coordinates, so that two distinct integral subschemes
cannot be equations of only $m$ of the $m+1$ coordinates.
\end{rem}

@@

\begin{lem}
\label{lem:bound-ker-chi}
Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has
extremal rays $e_0,\ldots, e_t$ in degrees $d_0, \ldots, d_t$ then $\ker \chi$
is generated in degrees at most $2(\sum_{i=0}^{t}d_i-1)$.
\end{lem}
\begin{proof}
Since $e_0, \ldots, e_t$ are extremal rays, Proposition
~\ref{prop:cone-generation} implies every element $\sigma \in \Sigma$ can be written
in a canonical form $\lambda + \sum_{i=0}^{t} \zeta_i e_i$ where all $\zeta_i \in \mathbb{Z}_{\ge 0}$.  Let
$\lambda_0 :=
0,\lambda_1, \ldots, \lambda_r$ be all elements of $\Sigma$ which
can be
written in the form $\lambda_j = \sum_{i=0}^{t}s_i e_i$ with $0
\leq s_i < 1.$ Then, for any $1 \leq j \leq k \leq r,$ we can write $\lambda_j + \lambda_k$ in
the above canonical form, yielding a (possibly trivial) relation in degree at most $\deg \lambda_j
+ \deg \lambda_k\leq 2 \cdot \left( \sum_{i=0}^{t}d_i -1 \right).$
Furthermore, these relations generate all relations, as one can apply a
sequence of these relations to put any $\sigma \in \Sigma$ into canonical form
$\sigma = \lambda + \sum_{i=0}^{t}\zeta_i e_i$ from Proposition
~\ref{prop:cone-generation}.
\end{proof}
\begin{lem}
\label{lem:proj-relations-psi}
Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m,$ where
$\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
$\ell_i = \lcm_{j \neq i} (k_j)$. Define $\Sigma$ as in Equation
~\eqref{eqn:Sigma-defn} and $\psi$ as ~\eqref{eqn:factor-through-semigroup-ring}. Then, $\ker \psi$ is generated in degrees at most
\begin{align}
\label{eqn:proj-relation-degree}
	\frac{\max_{0\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=0}^n \ell_i a_i.
\end{align}

@@

\noindent
lying in some degree $d \in \mathbb{N}$
with $c_j \ge -\alpha_j d$ (for all $j$) satisfying $\bida_i + \sum_{j = 1}
^n \bida_j c_j = 0$ and $\bidb_i + \sum_{j=1}^n \bidb_j c_j = 0$.
Specifically, $\beta_i$,
is the polynomial $\beta_i(z_1,z_2,z_3,z_4)$ so that
$\beta_i(z_1,z_2,z_3,z_4) - z_i \in \ker \psi$. Such an element
$\beta$ exists and is unique because rational functions
whose numerators are polynomials in $f_1,f_2,f_3,f_4$ form a basis
of all rational functions in $R_D$. Furthermore, these
generate all relations, since they allow us to reduce any monomial $u^d\prod_{j =
1}^n z_j^{r_j}$ to the canonical form where $r_j = - \lfloor d \alpha_i
\rfloor$
whenever $j > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(\beta_i  -z_i) \cap \ker(\psi)$ for each $i$.

To bound the degree of generation of the ideal 
$(\beta_i - z_i) \cap \ker(\psi)$, we fix $i \in \{1,\ldots, n\}$ and a relation of 
the form $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ {\bf for the remainder of the proof}.  Note that there 
are no relations for $i\in \{1, 2, 3, 4\}$ as then $\beta_i - z_i = 0 \in \bk[\Sigma]$. Thus we restrict attention to $i \ge 5$. Our goal 
is to show that if $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ has 
sufficiently high degree, then there is another relation dividing it. 
We do so by considering the lattice points corresponding to the 
monomials appearing in the relation $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$, and finding a fixed $\lambda\in \Sigma$
that we can simultaneously factor out of all monomials.

@@

Note that
\begin{align}
\label{eqn:e-bound}
	\deg(E) \le \rho + \begin{cases}
	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
	&\mbox{ if } i \in \Tp \\
	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
	&\mbox{ if } i \in \Tm. \end{cases}
\end{align}
where $\rho$ is as in Equation \ref{eqn:def-sigma}. To obtain the
bound given in Equation ~\eqref{eqn:e-bound}, the $\rho$ term corresponds to the sums of fractional parts of $s_j - r_j$'s and $s_{j,k} - r_{j,k}$'s, whereas the second term corresponds to the sums of $r_j$'s and $r_{j,k}$'s (noting that in equation \ref{eqn:hirz-E-translation} $s_j - \lfloor s_j - r_j \rfloor= r_j + \fr(s_j - r_j)$).

Define
\[
	\lambda := \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
\]

Let $M_i$ be the set of monomials terms of $\beta_i = \beta_i(z_1, \ldots z_4)$.  Let $\mu = \prod_{j=1}^4
{z_j}^{h_j}\in M_i$ and consider the lattice point 
\[
	\sigma_\mu = (d, c_1 + h_1, \ldots, c_4+h_4, c_5, \ldots, c_n).
\]
where $d = \deg \sigma$.
Define 
\[
	E_\mu = \sigma_\mu - \lambda.
\]
From the definitions, $E_\mu$ lies in $\Sigma$ 
and has the same degree as $E$.

@@

\section{Further Questions}
\label{sec:conc}
Recall that every minimal rational surface is either isomorphic to
$\bp^2$ or $\hirz_m$ for some $m \geq 0, m \neq 1$ \cite{eisenbud-harris:minimal}. By Theorems
~\ref{thm:proj-generators-relations} and ~\ref{thm:hirz-generators-relations}, we have given bounds for the generators and relations
of arbitrary canonical rings on any minimal rational surface. A
natural extension of our results is the following.
\begin{question}
\label{qn:general-minimal-surface}
Can we describe generators and relations of $R_D$ for $D$ a divisor on an
arbitrary rational surface $X$?
\end{question}

@@

\section{Acknowledgments}
\label{sec:ack}
We are grateful to David Zureick-Brown for offering great advice on
this project, for many useful suggestions on this paper, and for
many valuable conversations. We thank Peter
Landesman and Shou-Wu Zhang for offering helpful comments and
suggestions for this paper. We also thank Ken Ono and the
Emory University Number Theory REU for arranging our project and
for the great support that we have received. Finally, we would like to acknowledge the
support of the National Science Foundation (grant number DMS-1250467
).

>>>>

\usepackage{amsmath}
\usepackage{amsxtra}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{mathrsfs}
\usepackage{euler}
\usepackage{hyperref}
\usepackage{color}
\usepackage{longtable}
\usepackage{float}
\usepackage{caption}
\usepackage{thmtools}
\usepackage{thm-restate}

@@

In Section \ref{sec:proj} we prove the following two results bounding
the degree of generators and relations of
stacky canonical rings on $\bp^m$:
\begin{restatable}{thm}{restateeffective}
\label{thm:proj-effective-intro}
Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, with $\alpha_i =
\frac{c_i}{k_i} \in \bq_{> 0}$ and each $D_i \in \di \bp^m$ an integral divisor.

@@

\begin{restatable}{thm}{restateproj}
\label{thm:proj-generators-relations}
Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
as in Theorem ~\ref{thm:proj-effective-intro}. Write $\ell_i := \lcm
_{j \ne i}(k_j)$ and $a_i := \deg D_i$. Let $\bp^m \cong \proj
\bk[x_0, \ldots, x_m]$. Now suppose that $f_0, \ldots, f_n$ contain
$m$ independent linear polynomials in $x_0, \ldots, x_m$ (with possibly
zero coefficients $\alpha_j$).

Then $R_D$ is generated in degrees at most 
\[
	\sum_{i=0}^n \ell_i a_i
\]

\noindent
with relations generated in degrees at most
\[
	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0\le i \le n}
	(	\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
\]
\end{restatable}

\begin{rem}\label{rem:proj-tight-bounds} Note that the bounds
	given in Theorem ~\ref{thm:proj-effective-intro}
are tight and are typically attained, as explained in
Remark ~\ref{rem:exact-effective-bounds}.
Additionally, the bounds given in Theorem 
~\ref{thm:proj-generators-relations} are asymptotically
tight to within a factor of two 
for the following class of divisors. Consider
a divisor 
$ D = \sum_{i=0}^n\frac{p_i}{2q_i}H_i \in \bq \otimes_\bz \di \bp^m$
such that $H_i$ are hyperplanes,  
$q_i$ are pairwise coprime integers, and $p_i$ are chosen
so that $\deg D = \frac{1}{2 \prod_{i=0}^n}q_i$. Further,
choose a linear subspace $\pi: \bp^1 \rightarrow \bp^m$  generically so that
$\pi^* D = \sum_{i=0}^n \frac{p_i}{2q_i}P_i$, 
where $P_i$ are distinct points in $\bp^1$. To choose such a map
$\pi$, we may need to assume that the base field is infinite.
Note that by the Remark immediately following Theorem 8 in 
\cite{dorney:canonical},
the given bounds on the generators and relations of
$R_{\pi^*D}$ are within
a factor of two of the degree of generation and relations of
$R_{\pi^*D}$. Finally, since restriction map
$R_D \rightarrow R_{\pi^*D}$ induced by the restriction maps
on cohomology $H^0(\bp^m, dD) \rightarrow H^0(\bp^1, \pi^*(dD))
\cong H^0(\bp^1, d\pi^* D)$ are surjective, we obtain that
the bounds for the generators and relations of $R_D$ given in
Theorem ~\ref{thm:proj-generators-relations} also
agree with the degree of generation and relations 
to within a factor of two.
 \end{rem}

In Section \ref{sec:hirz}, we shift our attention to Hirzebruch surfaces. Recall that for each $m \geq 0$ we can define the
Hirzebruch surface $F_m := \proj(\sym^\bullet \sco_{\bp^1} \oplus
\sco_{\bp^1}(m)),$ or as a quotient of an open subscheme of
$\ba^4$ by a 
weighted action, as is done in the
beginning of Section \ref{sec:hirz}.
Note that Hirzebruch surfaces are regular, normal,
and locally factorial, being $\bp^1$-bundles over
$\bp^1$. Therefore,, the natural map from Cartier
divisors to Weil divisors is an isomorphism.
In other words, all Cartier divisors arise as the zero locus
of a section of some line bundle. We implicitly use this in the
statement of the following theorem. The analogous fact for
projective space was also implicitly used in Theorems
~\ref{thm:proj-effective-intro} and ~\ref{thm:proj-generators-relations}.

@@

\noindent
span $H^0(\bp^m, dD)$ over $\bk$. Furthermore, functions 
of the form $u^d \cdot \prod_{i=0}^n f_i^{c_i}$ satisfying Equation ~\eqref{align:pm-span} and
\begin{align}
\label{align:pm-basis}
c_i = -\lfloor d\alpha_i \rfloor && \text{ for } && i > m
\end{align}

@@

\begin{rem}
\label{rem:proj-two-points}
Note that we cannot extend this result to the case when
$D$ is supported at two hypersurfaces with arbitrary rational (non-effective)
coefficients in the same manner that O'Dorney does for the
$\bp^1$ case \cite[Section 4]{dorney:canonical}. As will be shown
in Example ~\ref{eg:hyperplane}, the degrees of generation of the
canonical ring of a general $\bq$-divisor supported on two
hyperplanes cannot be bounded so tightly. The two-point
$\bp^1$ result leverages the fact that $\bp^1$ has precisely two
independent coordinates, so that two distinct integral subschemes
cannot repreesnt equations of only $m$ of the $m+1$ coordinates.
\end{rem}

@@

\begin{lem}
\label{lem:bound-ker-chi}
Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has
extremal rays $e_0,\ldots, e_t$ in degrees $d_0, \ldots, d_t$ then $\ker \chi$
is generated in degrees at most $2(\sum_{i=0}^{t}d_i-1)$.
\end{lem}
\begin{proof}
Since $e_0, \ldots, e_t$ are extremal rays, Proposition
~\ref{prop:cone-generation} implies every element $\sigma \in \Sigma$ can be written
in a canonical form $\lambda + \sum_{i=0}^{t} \zeta_i e_i$ where all $\zeta_i \in \mathbb{Z}_{\ge 0}$.  Let
$\lambda_0 :=
0,\lambda_1, \ldots, \lambda_r$ be all elements of $\Sigma$ which
can be
written in the form $\lambda_j = \sum_{i=0}^{t}s_i e_i$ with $0
\leq s_i < 1.$ Then, for any $1 \leq j \leq k \leq r,$ we can write $\lambda_j + \lambda_k$ in
the above canonical form, yielding a (possibly trivial) relation in degree at most $\deg \lambda_j
+ \deg \lambda_k\leq 2 \cdot \left( \sum_{i=0}^{t}d_i -1 \right).$
Furthermore, these relations generate all relations, as one can apply a
sequence of these relations to put any $\sigma \in \Sigma$ into canonical form
$\sigma = \lambda + \sum_{i=0}^{t}\zeta_i e_i$ from Proposition
~\ref{prop:cone-generation}.
\end{proof}
\begin{lem}
\label{lem:proj-relations-psi}
Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, where
$\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
$\ell_i = \lcm_{j \neq i} (k_j)$. Define $\Sigma$ as in Equation
~\eqref{eqn:Sigma-defn} and $\psi$ as in Equation
~\eqref{eqn:factor-through-semigroup-ring}. Then, $\ker \psi$ is
generated in degrees at most
\begin{align}
\label{eqn:proj-relation-degree}
	\frac{\max_{0\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=0}^n \ell_i a_i.
\end{align}

@@

\noindent
lying in some degree $d \in \mathbb{N}$
with $c_j \ge -\alpha_j d$ (for all $j$) satisfying $\bida_i + \sum_{j = 1}
^n \bida_j c_j = 0$ and $\bidb_i + \sum_{j=1}^n \bidb_j c_j = 0$.
Specifically, $\beta_i$,
is the polynomial $\beta_i(z_1,z_2,z_3,z_4)$ so that
$\beta_i(z_1,z_2,z_3,z_4) - z_i \in \ker \psi$. Such an element
$\beta$ exists and is unique because rational functions
whose numerators are polynomials in $f_1, f_2, f_3, f_4$ form a basis
of all rational functions in $R_D$. Furthermore, these
generate all relations, since they allow us to reduce any monomial $u^d\prod_{j =
1}^n z_j^{r_j}$ to the canonical form where $r_j = -\lfloor d \alpha_i
\rfloor$ whenever $j > 4$. To bound the degree of generation of these relations,
we bound the degree of generation of the ideal $(\beta_i - z_i) \cap
\ker(\psi)$ for each $i$.

\textbf{For the remainder of this proof:} we fix $i \in \{1, \ldots,
n\}$ and fix a relation of the form $u^d (z_i - \beta_i) \prod_{j =
1}^n z_j^{c_j}$ as we seek to bound the degree of generation of the
ideal $(\beta_i - z_i) \cap \ker(\psi)$. Note that there are no
relations for $i\in \{1, 2, 3, 4\}$ as then $\beta_i - z_i = 0 \in
\bk[\Sigma]$. Thus we restrict attention to $i \ge 5$. Our goal is
to show that if $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ has
sufficiently high degree, then there is another relation dividing
it. We do so by considering the lattice points corresponding to the
monomials appearing in the relation $u^d(z_i - \beta_i)\prod_{j=1}^
n z_j^{c_j}$, and finding a fixed $\lambda\in \Sigma$ that we can
simultaneously factor out of all monomials.

@@

Note that
\begin{align}
\label{eqn:e-bound}
	\deg(E) \le \rho + \begin{cases}
	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
	&\mbox{ if } i \in \Tp \\
	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
	&\mbox{ if } i \in \Tm. \end{cases}
\end{align}

\noindent
where $\rho$ is as in Equation ~\eqref{eqn:def-sigma}. To obtain the
bound given in Equation ~\eqref{eqn:e-bound}, the $\rho$ term 
corresponds to the sums of fractional parts of $s_j - r_j$'s and $s_
{j, k} - r_{j, k}$'s whereas the second term corresponds to the sums 
of $r_j$'s and $r_{j, k}$'s (noting that in Equation
~\ref{eqn:hirz-E-translation}, $s_j - \lfloor s_j - r_j \rfloor =
r_j + \fr(s_j - r_j)$).

Define
\[
	\lambda := \sigma - E = \sum_{j \in \Te} (\lfloor s_j - r_j \rfloor)
	e_j + \sum_{\substack{j \in \Tp \\ k \in \Tm}} ( \lfloor s_{j, k} -
	r_{j, k} \rfloor) e_{j, k} \in \Sigma.
\]

\noindent
Let $M_i$ be the set of monomials terms of $\beta_i = \beta_i(z_1, \ldots z_4)$.  Let $\mu = \prod_{j=1}^4
{z_j}^{h_j}\in M_i$ and consider the lattice point 
\[
	\sigma_\mu = (d, c_1 + h_1, \ldots, c_4+h_4, c_5, \ldots, c_n).
\]
where $d = \deg \sigma$.
Define 
\[
	E_\mu = \sigma_\mu - \lambda.
\]
From the definitions, $E_\mu$ lies in $\Sigma$ 
and has the same degree as $E$.

@@

\section{Further Questions}
\label{sec:conc}
Recall that every minimal rational surface is either isomorphic to
$\bp^2$ or $\hirz_m$ for some $m \geq 0, m \neq 1$ \cite{eisenbud-harris:minimal}. By Theorems
~\ref{thm:proj-generators-relations} and ~\ref{thm:hirz-generators-relations}, we have given bounds for the generators and relations
of arbitrary canonical rings on any minimal rational surface. A
natural extension of our results is the following.
\begin{question}
\label{qn:general-minimal-surface}
Can we describe generators and relations of $R_D$ for a divisor $D$ on an
arbitrary rational surface $X$?
\end{question}

@@

\section{Acknowledgments}
\label{sec:ack}
We are grateful to David Zureick-Brown for offering great advice on
this project, for many useful suggestions on this paper, and for
many valuable conversations. We thank Peter
Landesman and Shou-Wu Zhang for offering helpful comments and
suggestions for this paper. We also thank Ken Ono and the
Emory University Number Theory REU for arranging our project and
for the great support that we have received. Finally, we would like to acknowledge the
support of the National Science Foundation (grant number DMS-1250467).
